### 2022-02-16 ms_body/manuscript.Rmd
Push MS edits before submission

A total of 103 native-range records for *D. rubiformis* were obtained from [@Adair2004]. A total of 452 invaded-range records to evaluate model transferability were taken from Impson, Kleinjan and Hoffmann (unpublished). Distribution maps for *D. rubiformis* for both native and invaded range are provided in Fig. 1.

@@

@@

```{r import_fig_4, echo = FALSE}
knitr::include_graphics(here::here("./ms_body/ms_figs/fig_4_auc.png"), dpi = NA)
```

@@

```{r import_fig_5, echo = FALSE}
knitr::include_graphics(here::here("./ms_body/ms_figs/fig_5_maxent_maps.png"), dpi = NA)
```

@@

@@

**Table S1**

```{r table_S1, echo = FALSE}
# Import data to make Table S1
tableS1_data <- readr::read_csv(here::here("./data/data_clean/table2_data.csv")) %>%
  janitor::clean_names()

# Create Table S1
tableS1 <- tableS1_data %>%
  knitr::kable(
    format = "latex",
    align = "l",
    booktabs = TRUE,
    longtable = TRUE,
    linesep = "",
    escape = FALSE,
    col.names = c(
      "Model",
      "RM",
      "FC",
      "AUC\\textsubscript{test}",
      "AUC\\textsubscript{diff}",
      "OR\\textsubscript{10}",
      "AIC\\textsubscript{c}"
    )
  ) %>%
  kableExtra::kable_styling(
    position = "left",
    latex_options = c("striped", "repeat_header")
    #,    stripe_color = "gray!15"
  )

# Display Table S1
tableS1
```

>>>>

A total of 103 native-range records for *D. rubiformis* were obtained from @Adair2004. A total of 452 invaded-range records to evaluate model transferability were taken from Impson, Kleinjan and Hoffmann (unpublished). Distribution maps for *D. rubiformis* for both native and invaded range are provided in Fig. 1.

@@

**Figure 1:** Distribution records for *Dasineura rubiformis* in its (a) native range (Australia), and (b) introduced range (South Africa). Filled black circles indicate field sites where *D. rubiformis* has been recorded, and filled grey circles indicate field sites where it was not found.

**Figure 2:** Model tuning experiments to identify optimal MaxEnt model settings configurations for *D. rubiformis* native-range (Australia) models. Model tuning was performed across a range of regularisation multipliers (0.5 - 10), and feature classes (H = Hinge, L = Linear, Q = Quadratic). Model performance and optimal settings configurations were assessed using multiple metrics that reflected aspects of model (1) discriminatory ability (AUC~test~), (2) overfitting (AUC~diff~), (3) omission rates (OR~10~), and (4) overall parsimony (AICc).

**Figure 3:** Relationships between MaxEnt climatic suitability scores (between the native and introduced range) and the probability of establishment for *D. rubiformis* in its introduced range. Five different MaxEnt models are compared, specified with either default MaxEnt settings, or four optimised settings configurations. Mean prediction curves $\pm$ 95% confidence intervals (indicated by grey-shaded ribbons) are derived from logistic General Linear Model's (GLM's).

**Figure 4::** MaxEnt model validation using out-of-sample Area under the Curve (AUC) and independent testing data from the introduced geographic range of *D. rubiformis* in South Africa. Five different MaxEnt models are compared, specified with either default MaxEnt settings, or four optimised settings configurations. The dashed horizontal line at y = 0.75 indicates the lowest bounds of acceptable model accuracy according to Fielding and Bell (1997). AUC values closer to 1 indicate improved model accuracy. Boxplots show the results obtained from n = 500 bootstrap resamples of the fitted logistic Generali Linear Models (GLM's). See text for further details.

**Figure 5::** Projected MaxEnt climatic similarity for *D. rubiformis* in its introduced range (South Africa) based on native-range MaxEnt models (Australia). Five different MaxEnt models are compared, specified with either default MaxEnt settings, or four optimised settings configurations. Climatic suitability scores closer to 1 indicate higher climatic similarity between climates in the introduced vs native-range.

**Figure 6:** Comparing *D. rubiformis* establishment in its introduced range (South Africa) given by MaxEnt model extrapolation. (a) Multivariate Environmental Similarity Surfaces (MESS) for *D. rubiformis*. MESS maps were thresholded to indicate regions where MaxEnt models were extrapolating (extrapolation - light grey fill) or not (interpolation - dark grey fill). (b) The probability that *D. rubiformis* was established or not at field sites in South Africa depending on whether the field site was in interpolation/extrapolation.

**Figure 7:** Projected MaxEnt climatic similarity for *D. rubiformis* in its introduced range (South Africa), thresholded to show geographic regions where the estimated probability of establishment for *D. rubiformis* was greater than 75% (i.e. MaxEnt score = 0.30, taken from Figure 4) (Suitable regions - dark grey fill) or not (unsuitable regions - light grey fill).

**Table 1:** Parameter estimates and Likelihood Ratio Tests (LRT's) comparing the relationships between MaxEnt climatic suitability scores (between the native and introduced range) and the probability of establishment for *D. rubiformis* in its introduced range. Five different MaxEnt models are compared, specified with either default MaxEnt settings, or four optimised settings configurations. $\\beta$\\textsuperscript{a} indicate the factor by which the probability of *D. rubiformis* establishment increases in South Africa for a 1% increase in climatic similarity between South Africa and its native-range (Australia). LRT's compare logistic General Linear Model's (GLM's) fitted with the climatic match score as a contiunous covariate and *D. rubiformis* establishment as a Boolean response variable against an analogous GLM fitted with a random intercept term only.

@@

```{r import_fig_4, out.width="80%", out.height="80%",  echo = FALSE}
knitr::include_graphics(here::here("./ms_body/ms_figs/fig_4_auc.png"), dpi = NA)
```

@@

```{r import_fig_5, out.width="100%", out.height="100%", echo = FALSE}
knitr::include_graphics(here::here("./ms_body/ms_figs/fig_5_maxent_maps.png"), dpi = NA)
```

@@

## *Figure 7*

```{r import_fig_7, echo = FALSE}
knitr::include_graphics(here::here("./ms_body/ms_figs/fig_7_biocontrol.png"), dpi = NA)
```

@@

### 2022-02-16 ms_body/manuscript.tex
Push MS edits before submission

A total of 103 native-range records for \emph{D. rubiformis} were
obtained from (Adair, 2004). A total of 452 invaded-range records to
evaluate model transferability were taken from Impson, Kleinjan and
Hoffmann (unpublished). Distribution maps for \emph{D. rubiformis} for
both native and invaded range are provided in Fig. 1.

@@

@@

\includegraphics{C:/Users/s1900332/OneDrive - Rhodes University/Manuscripts/MS-Dasinuera-MaxEnt-Transfer/./ms_body/ms_figs/fig_4_auc.png}

@@

\includegraphics{C:/Users/s1900332/OneDrive - Rhodes University/Manuscripts/MS-Dasinuera-MaxEnt-Transfer/./ms_body/ms_figs/fig_5_maxent_maps.png}

@@

@@

\textbf{Table S1}

\begin{longtable}[l]{lllllll}
\toprule
Model & RM & FC & AUC\textsubscript{test} & AUC\textsubscript{diff} & OR\textsubscript{10} & AIC\textsubscript{c}\\
\midrule
\endfirsthead
\multicolumn{7}{@{}l}{\textit{(continued)}}\\
\toprule
Model & RM & FC & AUC\textsubscript{test} & AUC\textsubscript{diff} & OR\textsubscript{10} & AIC\textsubscript{c}\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\cellcolor{gray!6}{Default} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{HLQPT} & \cellcolor{gray!6}{0.89} & \cellcolor{gray!6}{0.04} & \cellcolor{gray!6}{0.18} & \cellcolor{gray!6}{564.46}\\
AUCtest & 6 & H & 0.89 & 0.02 & 0.09 & 15.56\\
\cellcolor{gray!6}{AUCdiff} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{HLQPT} & \cellcolor{gray!6}{0.89} & \cellcolor{gray!6}{0.02} & \cellcolor{gray!6}{0.13} & \cellcolor{gray!6}{485.91}\\
OR10 & 6 & HLQPT & 0.92 & 0.02 & 0.11 & 144.39\\
\cellcolor{gray!6}{AICc} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{H} & \cellcolor{gray!6}{0.90} & \cellcolor{gray!6}{0.02} & \cellcolor{gray!6}{0.09} & \cellcolor{gray!6}{0.00}\\*
\end{longtable}

>>>>

A total of 103 native-range records for \emph{D. rubiformis} were
obtained from Adair (2004). A total of 452 invaded-range records to
evaluate model transferability were taken from Impson, Kleinjan and
Hoffmann (unpublished). Distribution maps for \emph{D. rubiformis} for
both native and invaded range are provided in Fig. 1.

@@

\textbf{Figure 1:} Distribution records for \emph{Dasineura rubiformis}
in its (a) native range (Australia), and (b) introduced range (South
Africa). Filled black circles indicate field sites where \emph{D.
rubiformis} has been recorded, and filled grey circles indicate field
sites where it was not found.

\textbf{Figure 2:} Model tuning experiments to identify optimal MaxEnt
model settings configurations for \emph{D. rubiformis} native-range
(Australia) models. Model tuning was performed across a range of
regularisation multipliers (0.5 - 10), and feature classes (H = Hinge, L
= Linear, Q = Quadratic). Model performance and optimal settings
configurations were assessed using multiple metrics that reflected
aspects of model (1) discriminatory ability (AUC\textsubscript{test}),
(2) overfitting (AUC\textsubscript{diff}), (3) omission rates
(OR\textsubscript{10}), and (4) overall parsimony (AICc).

\textbf{Figure 3:} Relationships between MaxEnt climatic suitability
scores (between the native and introduced range) and the probability of
establishment for \emph{D. rubiformis} in its introduced range. Five
different MaxEnt models are compared, specified with either default
MaxEnt settings, or four optimised settings configurations. Mean
prediction curves \(\pm\) 95\% confidence intervals (indicated by
grey-shaded ribbons) are derived from logistic General Linear Model's
(GLM's).

\textbf{Figure 4::} MaxEnt model validation using out-of-sample Area
under the Curve (AUC) and independent testing data from the introduced
geographic range of \emph{D. rubiformis} in South Africa. Five different
MaxEnt models are compared, specified with either default MaxEnt
settings, or four optimised settings configurations. The dashed
horizontal line at y = 0.75 indicates the lowest bounds of acceptable
model accuracy according to Fielding and Bell (1997). AUC values closer
to 1 indicate improved model accuracy. Boxplots show the results
obtained from n = 500 bootstrap resamples of the fitted logistic
Generali Linear Models (GLM's). See text for further details.

\textbf{Figure 5::} Projected MaxEnt climatic similarity for \emph{D.
rubiformis} in its introduced range (South Africa) based on native-range
MaxEnt models (Australia). Five different MaxEnt models are compared,
specified with either default MaxEnt settings, or four optimised
settings configurations. Climatic suitability scores closer to 1
indicate higher climatic similarity between climates in the introduced
vs native-range.

\textbf{Figure 6:} Comparing \emph{D. rubiformis} establishment in its
introduced range (South Africa) given by MaxEnt model extrapolation. (a)
Multivariate Environmental Similarity Surfaces (MESS) for \emph{D.
rubiformis}. MESS maps were thresholded to indicate regions where MaxEnt
models were extrapolating (extrapolation - light grey fill) or not
(interpolation - dark grey fill). (b) The probability that \emph{D.
rubiformis} was established or not at field sites in South Africa
depending on whether the field site was in interpolation/extrapolation.

\textbf{Figure 7:} Projected MaxEnt climatic similarity for \emph{D.
rubiformis} in its introduced range (South Africa), thresholded to show
geographic regions where the estimated probability of establishment for
\emph{D. rubiformis} was greater than 75\% (i.e.~MaxEnt score = 0.30,
taken from Figure 4) (Suitable regions - dark grey fill) or not
(unsuitable regions - light grey fill).

\textbf{Table 1:} Parameter estimates and Likelihood Ratio Tests (LRT's)
comparing the relationships between MaxEnt climatic suitability scores
(between the native and introduced range) and the probability of
establishment for \emph{D. rubiformis} in its introduced range. Five
different MaxEnt models are compared, specified with either default
MaxEnt settings, or four optimised settings configurations.
\(\\beta\)\textbackslash textsuperscript\{a\} indicate the factor by
which the probability of \emph{D. rubiformis} establishment increases in
South Africa for a 1\% increase in climatic similarity between South
Africa and its native-range (Australia). LRT's compare logistic General
Linear Model's (GLM's) fitted with the climatic match score as a
contiunous covariate and \emph{D. rubiformis} establishment as a Boolean
response variable against an analogous GLM fitted with a random
intercept term only.

@@

\includegraphics[width=0.8\linewidth,height=0.8\textheight]{C:/Users/s1900332/OneDrive - Rhodes University/Manuscripts/MS-Dasinuera-MaxEnt-Transfer/./ms_body/ms_figs/fig_4_auc}

@@

\includegraphics[width=1\linewidth,height=1\textheight]{C:/Users/s1900332/OneDrive - Rhodes University/Manuscripts/MS-Dasinuera-MaxEnt-Transfer/./ms_body/ms_figs/fig_5_maxent_maps}

@@

\hypertarget{figure-7}{%
\subsection{\texorpdfstring{\emph{Figure 7}}{Figure 7}}\label{figure-7}}

\includegraphics{C:/Users/s1900332/OneDrive - Rhodes University/Manuscripts/MS-Dasinuera-MaxEnt-Transfer/./ms_body/ms_figs/fig_7_biocontrol.png}

@@
